### 2022-08-17 ersteops/templates/printpdf/paperless_template.tex
clean no need packages
change fontface

%prescription_latex.tex
{% autoescape on %}
\documentclass{article}
\usepackage[utf8]{inputenc}
\usepackage[spanish]{babel}
\usepackage[T1]{fontenc}
\usepackage{textcomp}
\usepackage{graphicx}
\usepackage{eso-pic}
\usepackage{ifthen}
\usepackage[abs]{overpic}
\usepackage{pict2e,xcolor,varwidth}
\usepackage{color}
\usepackage{layout}
%\usepackage{tikz}
%\usepackage{relsize}
\usepackage{etoolbox}
\usepackage[paperwidth=27.94cm, paperheight=21.59cm, left=0.0cm,right=0.0cm,top=0.0in,bottom=0.0in,headheight=0in,headsep=0pt,footskip=120pt]{geometry}
% Check parameters in: https://en.wikibooks.org/wiki/LaTeX/Page_Layout
%{# Define where latex finds images #}
{{ latex_graphics_path }}
%\setmainfont{Arial}
%\usepackage{fancyhdr}
\usepackage{uarial}
%\usepackage[scaled]{uarial}
\usepackage{transparent}
\usepackage[protrusion=true,expansion=true]{microtype}
\usepackage{calc}
\usepackage{verbatim}
\makeatletter
\g@addto@macro\@verbatim\small
\makeatother 
\usepackage{xcolor}

\usepackage{lmodern}
%\fontfamily{lmss}\selectfont
\usepackage[utf8]{inputenc}
%\usepackage{unixode}

@@

    \put(0.53673588,0.1536906){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont {{content.electro_rhythm}}\end{tabular}}}}%    
    \put(0.63974772,0.15416371){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont {{content.electro_frequency}}\end{tabular}}}}%
    \put(0.73901494,0.1542802){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont {{content.electro_wave_p}}\end{tabular}}}}%
    \put(0.80638047,0.15431264){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont {{content.electro_pr}}\end{tabular}}}}%
    \put(0.54883898,0.14280022){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont {{content.electro_axis_qrs}}\end{tabular}}}}%
    \put(0.61275927,0.14232657){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont {{content.electro_qrs}}\end{tabular}}}}%
    \put(0.66200174,0.1423264){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont {{content.electro_st}}\end{tabular}}}}%
    \put(0.7368123,0.14137953){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont {{content.electro_wave_t}}\end{tabular}}}}%
    \put(0.809729,0.1423264){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont {{content.electro_qt}}\end{tabular}}}}%    
    \put(0.49140242,0.11457272){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont {{content.electro_abnormalities}}\end{tabular}}}}%
    \put(0.49140242,0.04639155){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont {{content.electro_interpretation}} {{content.json_physical_exploration}}\end{tabular}}}}%

>>>>

%prescription_latex.tex
{% autoescape on %}
\documentclass{article}
\usepackage[utf8]{inputenc}
\usepackage[spanish]{babel}
\usepackage[T1]{fontenc}
\usepackage{textcomp}
\usepackage{graphicx}
\usepackage{eso-pic}
\usepackage{ifthen}
\usepackage[abs]{overpic}
\usepackage{pict2e,xcolor,varwidth}
\usepackage{color}
\usepackage{layout}
%\usepackage{tikz}
%\usepackage{relsize}
%\usepackage{etoolbox}
\usepackage[paperwidth=27.94cm, paperheight=21.59cm, left=0.0cm,right=0.0cm,top=0.0in,bottom=0.0in,headheight=0in,headsep=0pt,footskip=120pt]{geometry}
% Check parameters in: https://en.wikibooks.org/wiki/LaTeX/Page_Layout
%{# Define where latex finds images #}
{{ latex_graphics_path }}
%\setmainfont{Arial}
%\usepackage{fancyhdr}
%\usepackage{uarial}
%\usepackage[scaled]{uarial}
\usepackage{transparent}
%\usepackage[protrusion=true,expansion=true]{microtype}
%\usepackage{calc}
%\usepackage{verbatim}
%\makeatletter
%\g@addto@macro\@verbatim\small
%\makeatother 
\usepackage{xcolor}

%\usepackage{lmodern}
%\fontfamily{lmss}\selectfont
%\usepackage[utf8]{inputenc}
%\usepackage{unixode}

@@

    \put(0.53673588,0.1536906){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{qcr}\selectfont {{content.electro_rhythm}}\end{tabular}}}}%    
    \put(0.63974772,0.15416371){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{qcr}\selectfont {{content.electro_frequency}}\end{tabular}}}}%
    \put(0.73901494,0.1542802){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{qcr}\selectfont {{content.electro_wave_p}}\end{tabular}}}}%
    \put(0.80638047,0.15431264){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{qcr}\selectfont {{content.electro_pr}}\end{tabular}}}}%
    \put(0.54883898,0.14280022){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{qcr}\selectfont {{content.electro_axis_qrs}}\end{tabular}}}}%
    \put(0.61275927,0.14232657){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{qcr}\selectfont {{content.electro_qrs}}\end{tabular}}}}%
    \put(0.66200174,0.1423264){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{qcr}\selectfont {{content.electro_st}}\end{tabular}}}}%
    \put(0.7368123,0.14137953){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{qcr}\selectfont {{content.electro_wave_t}}\end{tabular}}}}%
    \put(0.809729,0.1423264){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{qcr}\selectfont {{content.electro_qt}}\end{tabular}}}}%    
    \put(0.49140242,0.11457272){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{qcr}\selectfont {{content.electro_abnormalities}}\end{tabular}}}}%
    \put(0.49140242,0.04639155){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{qcr}\selectfont {{content.electro_interpretation}} {{content.json_physical_exploration}}\end{tabular}}}}%

### 2022-08-17 ersteops/templates/printpdf/rendered_template.tex
clean no need packages
change fontface

\documentclass{article}
\usepackage[utf8]{inputenc}
\usepackage[spanish]{babel}
\usepackage[T1]{fontenc}
\usepackage{textcomp}
\usepackage{graphicx}
\usepackage{eso-pic}
\usepackage{ifthen}
\usepackage[abs]{overpic}
\usepackage{pict2e,xcolor,varwidth}
\usepackage{color}
\usepackage{layout}
%\usepackage{tikz}
%\usepackage{relsize}
\usepackage{etoolbox}
\usepackage[paperwidth=27.94cm, paperheight=21.59cm, left=0.0cm,right=0.0cm,top=0.0in,bottom=0.0in,headheight=0in,headsep=0pt,footskip=120pt]{geometry}
% Check parameters in: https://en.wikibooks.org/wiki/LaTeX/Page_Layout
%
\graphicspath{ {/vagrant/ersteops/static/img/printpdf/} }
%\setmainfont{Arial}
%\usepackage{fancyhdr}
\usepackage{uarial}
%\usepackage[scaled]{uarial}
\usepackage{transparent}
\usepackage[protrusion=true,expansion=true]{microtype}
\usepackage{calc}
\usepackage{verbatim}
\makeatletter
\g@addto@macro\@verbatim\small
\makeatother 
\usepackage{xcolor}

\usepackage{lmodern}
%\fontfamily{lmss}\selectfont
\usepackage[utf8]{inputenc}
%\usepackage{unixode}

@@

    \put(0.53673588,0.1536906){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont NA\end{tabular}}}}%    
    \put(0.63974772,0.15416371){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont NA\end{tabular}}}}%
    \put(0.73901494,0.1542802){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont NA\end{tabular}}}}%
    \put(0.80638047,0.15431264){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont NA\end{tabular}}}}%
    \put(0.54883898,0.14280022){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont NA\end{tabular}}}}%
    \put(0.61275927,0.14232657){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont NA\end{tabular}}}}%
    \put(0.66200174,0.1423264){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont NA\end{tabular}}}}%
    \put(0.7368123,0.14137953){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont NA\end{tabular}}}}%
    \put(0.809729,0.1423264){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont NA\end{tabular}}}}%    
    \put(0.49140242,0.11457272){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont NA\end{tabular}}}}%
    \put(0.49140242,0.04639155){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont NA \end{tabular}}}}%

>>>>

\documentclass{article}
\usepackage[utf8]{inputenc}
\usepackage[spanish]{babel}
\usepackage[T1]{fontenc}
\usepackage{textcomp}
\usepackage{graphicx}
\usepackage{eso-pic}
\usepackage{ifthen}
\usepackage[abs]{overpic}
\usepackage{pict2e,xcolor,varwidth}
\usepackage{color}
\usepackage{layout}
%\usepackage{tikz}
%\usepackage{relsize}
%\usepackage{etoolbox}
\usepackage[paperwidth=27.94cm, paperheight=21.59cm, left=0.0cm,right=0.0cm,top=0.0in,bottom=0.0in,headheight=0in,headsep=0pt,footskip=120pt]{geometry}
% Check parameters in: https://en.wikibooks.org/wiki/LaTeX/Page_Layout
%
\graphicspath{ {/vagrant/ersteops/static/img/printpdf/} }
%\setmainfont{Arial}
%\usepackage{fancyhdr}
%\usepackage{uarial}
%\usepackage[scaled]{uarial}
\usepackage{transparent}
%\usepackage[protrusion=true,expansion=true]{microtype}
%\usepackage{calc}
%\usepackage{verbatim}
%\makeatletter
%\g@addto@macro\@verbatim\small
%\makeatother 
\usepackage{xcolor}

%\usepackage{lmodern}
%\fontfamily{lmss}\selectfont
%\usepackage[utf8]{inputenc}
%\usepackage{unixode}

@@

    \put(0.53673588,0.1536906){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{qcr}\selectfont NA\end{tabular}}}}%    
    \put(0.63974772,0.15416371){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{qcr}\selectfont NA\end{tabular}}}}%
    \put(0.73901494,0.1542802){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{qcr}\selectfont NA\end{tabular}}}}%
    \put(0.80638047,0.15431264){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{qcr}\selectfont NA\end{tabular}}}}%
    \put(0.54883898,0.14280022){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{qcr}\selectfont NA\end{tabular}}}}%
    \put(0.61275927,0.14232657){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{qcr}\selectfont NA\end{tabular}}}}%
    \put(0.66200174,0.1423264){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{qcr}\selectfont NA\end{tabular}}}}%
    \put(0.7368123,0.14137953){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{qcr}\selectfont NA\end{tabular}}}}%
    \put(0.809729,0.1423264){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{qcr}\selectfont NA\end{tabular}}}}%    
    \put(0.49140242,0.11457272){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{qcr}\selectfont NA\end{tabular}}}}%
    \put(0.49140242,0.04639155){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{qcr}\selectfont NA \end{tabular}}}}%
